BioTime

### 2021-03-11 analysis/01_filter_by_traits.Rmd
allow 75% trait coverage

`id` is `NA` if there was no `id` match
`biotimeName` or `traitName` is `NA` if that ID is the result of an average of multliple species matches
`scientificName` is `NA` when there was no trait data for a given ID
```{r}
#set coverage threshold for analysis dataset
percent <- 0.85

@@

```{r}
usethis::use_data(biotime_traits)
pins::pin(biotime_traits, board = "github")
```

>>>>

`id` is `NA` if there was no `id` match
`biotimeName` or `traitName` is `NA` if that ID is the result of an average of multliple species matches
`scientificName` is `NA` when there was no trait data for a given ID
```{r}
#set coverage threshold for analysis dataset
percent <- 0.75

@@

### 2021-03-11 data-raw/02_biotime_ids.Rmd
allow 75% trait coverage

### Or, from the grid processing script
```{r}
#file created by 01_biotime_grid.R
bt_grid <- pins::pin_get("bt-grid", board = "github_data")

@@

Add the unresolved ID to all the other ids and join with biotime data
```{r}
biotime_ids <- unres %>%
  left_join(biotime_ids) %>% #join ID's back with all the columns
  filter(acceptedNameUsageID %in% c(
    "ITIS:1026896", #accepted on the ITIS website 
    "ITIS:172921", 
    "ITIS:508923",
    "ITIS:527684", 
    "ITIS:782604", 
    "ITIS:159807", 
    "ITIS:28034"
  )) %>%
  bind_rows(biotime_ids %>% filter(!sort %in% unres$sort)) #join to resolved ID's, excluding the observations we resolved manually

>>>>

### Or, from the grid processing script
```{r}
#file created by 01_biotime_grid.R
pins::board_register_github(repo = "karinorman/biodivTS_data", branch = "master", name = "github")
bt_grid <- pins::pin_get("bt-grid", board = "github")

@@

Add the unresolved ID to all the other ids and join with biotime data
```{r}
biotime_ids <- unres %>%
  left_join(biotime_ids) %>% #join ID's back with all the columns
  filter(acceptedNameUsageID %in% c(
    "ITIS:1026896", #accepted on the ITIS website 
    "ITIS:172921", 
    "ITIS:508923",
    "ITIS:527684", 
    "ITIS:782604", 
    "ITIS:159807", 
    "ITIS:28034",
    "ITIS:71868",
    "ITIS:683103"
  )) %>%
  bind_rows(biotime_ids %>% filter(!sort %in% unres$sort)) #join to resolved ID's, excluding the observations we resolved manually
